---
title: "First Text-mining Notebook"
output: html_notebook
---
Captured from the book "Ted Kwartler - Text Mining in Practice with R-Wiley (2017)"
## Chapter 2
```{r}
# Set Option
options(stringAsFactors=F)
Sys.setlocale('LC_ALL', 'C')
```


```{r}
library(stringi)
library(stringr)
library(qdap)
```

```{r}
text.df = read.csv('oct_delta.csv')
nchar(head(text.df$text))
mean(nchar(text.df$text))

# Only keeps document with the number of character greater than 0
subset.doc = subset(text.df, nchar(text.df$text)>0)
```

The function ```sub``` looks for the first pattern match in a string and replaces it.
Replacing the first string to the second string.
```{r}
sub('thanks', 'thank you', text,df[1,5], ignore.case=T)
```

It is also vectored so that it can be applied to a column and replacements will occur for each of the first pattern matches by row.
```{r}
sub('pls', 'please', text.df[1:5,5], ignore.case=F)
```

while the function ```gsub``` is the global substitution that can replace all instances. Compare:
```{r}
sub('text mining', 'tm', fake.text, ignore.case=F)
gsub('text mining', 'tm', fake.text, ignore.case=F)

```

The fucntion ```mgsub``` is multiple global substitution that allows to pass a vetor of patterns to be replaced with another vector.
```{r}
library(qdap)
patterns=c('good', 'also', 'text mining')
replacements = c('great', 'just as suitable', 'tm')
mgsub(patterns, replacements, fake.text)
```

### Example on replacing vectors
```{r}
patterns = c('Jan','Feb','Mar','Apr','May','Jun','Jul','Aug','Sep','Oct','Nov','Dec')
replacements=seq(1:12)
text.df$month=mgsub(patterns, replacements, text.df$month)
text.df$combined = paste(text.df$month, text.df$date, text.df$year, sep='-')
```

```{r}
library(lubridate)
#Converting date to official date
text.df$combined = mdy(text.df$combined)
```

```strsplit``` Function create subset string by matching character patterns. Where adding brackets let R treat * as character
```{r}
agents = strspit(text.df$text,'[*]')
```

Finding the characters from specific positions. Space also count.
```{r}
substring('R text mining is great', 18, 22)
```

