---
title: "First Text-mining Notebook"
output: html_notebook
---
Captured from the book "Ted Kwartler - Text Mining in Practice with R-Wiley (2017)"
# Chapter 2
## Chapter 2.4 String Manipulations
```{r}
# Set Option
options(stringAsFactors=F)
Sys.setlocale('LC_ALL', 'C')
```

```{r}
library(stringi)
library(stringr)
library(qdap)
```

```{r}
text.df = read.csv('oct_delta.csv')
nchar(head(text.df$text))
mean(nchar(text.df$text))

# Only keeps document with the number of character greater than 0
subset.doc = subset(text.df, nchar(text.df$text)>0)
```

The function ```sub``` looks for the first pattern match in a string and replaces it.
Replacing the first string to the second string.
```{r}
sub('thanks', 'thank you', text,df[1,5], ignore.case=T)
```

It is also vectored so that it can be applied to a column and replacements will occur for each of the first pattern matches by row.
```{r}
sub('pls', 'please', text.df[1:5,5], ignore.case=F)
```

while the function ```gsub``` is the global substitution that can replace all instances. Compare:
```{r}
sub('text mining', 'tm', fake.text, ignore.case=F)
gsub('text mining', 'tm', fake.text, ignore.case=F)

```

The fucntion ```mgsub``` is multiple global substitution that allows to pass a vetor of patterns to be replaced with another vector.
```{r}
library(qdap)
patterns=c('good', 'also', 'text mining')
replacements = c('great', 'just as suitable', 'tm')
mgsub(patterns, replacements, fake.text)
```

### Example on replacing vectors
```{r}
patterns = c('Jan','Feb','Mar','Apr','May','Jun','Jul','Aug','Sep','Oct','Nov','Dec')
replacements=seq(1:12)
text.df$month=mgsub(patterns, replacements, text.df$month)
text.df$combined = paste(text.df$month, text.df$date, text.df$year, sep='-')
```

```{r}
library(lubridate)
#Converting date to official date
text.df$combined = mdy(text.df$combined)
```

```strsplit``` Function create subset string by matching character patterns. Where adding brackets let R treat * as character
```{r}
agents = strspit(text.df$text,'[*]')
```

Finding the characters from specific positions. Space also count.
```{r}
substring('R text mining is great', 18, 22)
```

The ```last.chars``` function creats the numbers for substring dynamically.
```{r}
last.chars = function(text,num){
  last=substr(text, nchar(text)-num+1, nchar(text))
  return(last)
}

last.chars('R text mining is great', 5)
```

## Chapter 2.5 Keyword Scanning
Using ```grep``` function will return the position of the keyword
```{r}
grep('sorry', text.df$text, ignore.case=T)
```

Using ```grepl``` will return a logical vector 
```{r}
sorry = grepl('sorry', text.df$text, ignore.case=T)
sum(sorry/nrow(text.df))
```

Comfirming how often an agent sharing hyperlinks and phone number
```{r}
sum(grepl('http', tet.df$text, ignore.case=T))/nrow(text.df)
sum(grepl('[0-9]{3}|[0-9]{4}', text.df$text))/nrow(text.df)
```

## Chapter 2.6 tring Packages ```stringr``` and ```stringi```

```stri_count``` returns frequency count for the exact search terms.
```{r}
library(stringi)
stri_count(text.df$text, fixed='http')
```

Below returns a logical vector looking or the character pattern "http" within your tweets.
```{r}
library(stringr)
str_detect(text.df$text, 'http')
patterns = with(text.df, str_detect(text.df$text, 'http') & str_detect(text.df$text, 'DM'))
text.df[patterns,5]
```

## Chapter 2.7 Preprocessing Steps for Bag of Words Text Mining
```{r}
options(stringsAsFactors = FALSE)
Sys.setlocale('LC_ALL', 'C')
library(tm)
library(stringi)
tweets = data.frame(ID=seq(1:nrow(text.df)), text=text.df$text)
```

